My title

### 2024-12-01 paper/paper.qmd
Added causal modeL

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(dplyr)
library(knitr)

@@

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

number_of_cases_city |>
  ggplot(mapping = aes(x = arrest_was_not_made, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Status of the homicide case", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```

>>>>

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(dplyr)
library(knitr)
library(DiagrammeR)
library(rsvg)
library(DiagrammeRsvg)
library(png)

@@

Based on

@@

```{r}
#| label: fig-causal-model
#| fig-cap: Causal relationship between homicide case information and homicide case being unsolved 
#| echo: false
#| warning: false
#| message: false

# Referenced code from: https://stackoverflow.com/questions/42737645/how-to-export-images-of-diagrammer-in-r and https://www.erikigelstrom.com/articles/causal-graphs-in-r-with-diagrammer/
causal_model <- "digraph { graph []
  # Nodes
  node [shape = plaintext]
    A [label = 'Case being unsolved']
    B [label = 'Race of victim']
    C [label = 'Age of victim']
    D [label = 'Sex of victim']
    E [label = 'City']
    F [label = 'Date (Year)']
    G [label = 'Resources of investigating team (Confounder)']
  edge []
    B->A
    C->A
    D->A
    E->A
    F->A
{ rank = same; }
  # Confounding variables's edges 
  edge [style = dashed]
    G -> A
    G -> E
    G -> F
}"
# Export diagram as a png
exporting_image <- grViz(causal_model) |>
  export_svg() |>
  charToRaw() |>
  rsvg_png("../other/sketches/casual_model.png", width = 1000)

# NOTE: Needed to save diagram and read it in as an image since grViz doesn't render in PDFs
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("../other/sketches/casual_model.png")
plot.new()
rasterImage(the_image, 0,0,1.05,1)
```
RSME calculation

@@

number_of_cases_city |>
  ggplot(mapping = aes(x = arrest_was_not_made, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city)) +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Status of the homicide case", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```
